\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-03-20 paper/main.tex
Updated bug types

\tname\ contains \numbugs{} instances of reproducible bugs
representing three popular DL libraries, namely, \jax, \tf, and
\torch. Table~\ref{table:bug-characterization} shows the list of bug
instances for each supported library. Column ``\#'' shows the number
of bug instances, column ``build'' shows the breakdown of instances
for each kind of build, and column ``environment'' shows the breakdown
of instances for each kind of environment to reproduce the bug. Co-incidentally,
all bugs that require a GPU build are reproduced using a docker
container i.e. the column venv-docker is the same as bugs reproducible with CPU-GPU builds
of the libraries respectively. Table~\ref{table:bug-stats} shows whay type of error is manifested
due to each bug instance. In total, we have 15 different types of bug manifestations across
the three libraries.

@@

% Among these confirmed bug reports, we choose
% the ones that have enough information to reproduce the bugs, i.e.,
% code to reproduce the bug, dependencies required for the bug
% reproduction
% \Fix{Abid, can you confirm that environment here is not
%   the same as venv-docker that we are using on Table 1? instead it
%   means the version of CUDA, libraries, etc.? If so, avoid (re)using the
%   word environment.}
% , clear description of the desired behavior,
% etc. 
Afterwards, we assess the reproducibility of the bug by creating a
virtual environment that contains the necessary dependencies to
reproduce the bug.
Once we can successfully reproduce the bug by creating the
enviroment detailed in the report, we choose the bug to be included in
our dataset. Through this process, we end up with \numtorchselected{},
\numtfselected{}, and \numjaxselected{} bug instances for \torch, \tf,
and \jax, respectively.

@@

\begin{table}
  \centering
  \caption{\label{table:bug-stats}Different bug manifestation types from \tname.}
  \begin{tabular}{lrrrr}\toprule
    Bug manifestation type &Jax &Pytorch &Tensorflow \\\midrule
    Internal Exception &11 &9 &1 \\
    Incorrect Output &14 &11 &5 \\
    Value Error &7 &0 &3 \\
    Type Error &3 &2 &3 \\
    Attribute Error &2 &0 &0 \\
    Index Error &2 &1 &0 \\
    Floating Point Error &1 &0 &0 \\
    Error Not Raised &1 &0 &0 \\
    Parse Error &1 &0 &0 \\
    Runtime Error &1 &7 &1 \\
    Not Implemented Error &1 &0 &0 \\
    Memory Error &1 &1 &0 \\
    Invalid Argument Error &1 &0 &1 \\
    Crash &0 &4 &10 \\
    Assertion Error &0 &2 &0 \\
    \midrule
    $\Sigma$ &46 &37 &24 \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\tname\ contains \numbugs{} instances of reproducible bugs
representing three popular DL libraries, namely, \jax, \tf, and
\torch. Table~\ref{table:bug-characterization} shows the list of bug
instances for each supported library. Column ``\#'' shows the number
of bug instances, column ``build'' shows the breakdown of instances
for each kind of build, and column ``environment'' shows the breakdown
of instances for each kind of environment to reproduce the bug. Co-incidentally,
all bugs that require a GPU build are reproduced using a docker
container i.e. the column venv-docker is the same as bugs reproducible with CPU-GPU builds
of the libraries respectively. Table~\ref{table:bug-stats} shows whay type of error is manifested
due to each bug instance. In total, we have \numbugtypes\ different types of bug manifestations across
the three libraries.

@@

% Among these confirmed bug reports, we choose
% the ones that have enough information to reproduce the bugs, i.e.,
% code to reproduce the bug, dependencies required for the bug
% reproduction
% \Fix{Abid, can you confirm that environment here is not
%   the same as venv-docker that we are using on Table 1? instead it
%   means the version of CUDA, libraries, etc.? If so, avoid (re)using the
%   word environment.}
% , clear description of the desired behavior,
% etc. 
Afterwards, we assess the reproducibility of the bug by creating a
virtual environment that contains the necessary dependencies to
reproduce the bug.
Once we can successfully reproduce the bug by creating the
enviroment detailed in the report, we choose the bug to be included in
our dataset. Through this process, we end up with \numtorchbugs{},
\numtfbugs{}, and \numjaxbugs{} bug instances for \torch, \tf,
and \jax, respectively.

@@

\begin{table}
  \centering
  \caption{\label{table:bug-stats}Different bug manifestation types from \tname.}
  \begin{tabular}{lrrrr}\toprule
    Bug manifestation type &Jax &Pytorch &Tensorflow \\\midrule
    Incorrect Output &14 &11 &5 \\
    Internal Exception &11 &9 &4 \\
    Value Error &7 &0 &4 \\
    Type Error &3 &2 &3 \\
    Attribute Error &2 &0 &2 \\
    Index Error &2 &1 &0 \\
    Floating Point Error &1 &0 &0 \\
    Error Not Raised &1 &0 &0 \\
    Parse Error &1 &0 &0 \\
    Runtime Warning &1 &0 &0 \\
    Not Implemented Error &1 &0 &0 \\
    Memory Error &1 &1 &0 \\
    Invalid Argument Error &1 &0 &1 \\
    Runtime Error &0 &7 &1 \\
    Assertion Error &0 &2 &0 \\
    Segmentation Fault &0 &2 &1 \\
    Floating Point Exception &0 &1 &0 \\
    Aborted &0 &1 &8 \\
    \midrule
    $\Sigma$ &\numjaxbugs{} &\numtorchbugs{} &\numtfbugs{} \\
    \bottomrule
  \end{tabular}
\end{table}
